---
title: "Covid-19 Community Case Tracker"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About
While many sources are providing data about Covid-19 cases in the UK, it is not so easy to find comprehensive data about cases in specific counties. This website aims to provide visualisations of the Covid-19 data for the county you live in, so you can see if the response in your community is helping to flatten your county's curve. 

## Oxfordshire

You can also embed plots, for example:

```{r, echo = FALSE,  warning = FALSE}
load("oxford_data.Rda")
library(dplyr, warn.conflict = FALSE)
last_point <- df %>% # last trading day
  slice(which.max(dates))
library(ggplot2, warn.conflict = FALSE)
library(bbplot, warn.conflict = FALSE)
ggplot(df, aes(x = dates, y = oxford_cases)) +
geom_line(colour = "#007f7f", size = 1) +
geom_hline(yintercept = 0, size = 1, colour="#333333") +
labs(x = "Date", y = "Oxfordshire Covid-19 Cases", title = "Oxfordshire Covid-19 Cases (Linear)") +
scale_x_date(date_breaks = "3 days", date_labels = "%d/%m") + 
theme(axis.text.x = element_text(angle = 90)) +
geom_point(data = last_point, aes(x = dates, y = oxford_cases), col = "#007f7f", shape = 21, fill = "white", size = 2, stroke = 1.7) +
geom_text(data = last_point, aes(x = dates, y = oxford_cases, label = oxford_cases), size = 6, vjust = 2.0, nudge_x = 0.5) +
bbc_style() +
theme(plot.title = element_text(hjust = 0.5, size=20)) 

ggplot(df, aes(x = dates, y = oxford_cases)) +
geom_abline(intercept = 10, slope=2) +
geom_line(colour = "#007f7f", size = 1) +
geom_hline(yintercept = 0, size = 1, colour="#333333") +
labs(x = "Date", y = "Oxfordshire Covid-19 Cases", title = "Oxfordshire Covid-19 Cases (Log)") +
scale_x_date(date_breaks = "3 days", date_labels = "%d/%m") + 
scale_y_continuous(trans = 'log2') +
theme(axis.text.x = element_text(angle = 90)) +
geom_point(data = last_point, aes(x = dates, y = oxford_cases), col = "#007f7f", shape = 21, fill = "white", size = 2, stroke = 1.7) +
geom_text(data = last_point, aes(x = dates, y = oxford_cases, label = oxford_cases), size = 6, vjust = 2.0, nudge_x = 0.5) +
bbc_style() +
theme(plot.title = element_text(hjust = 0.5, size=20)) 
```


